Formulating and Validating RDF Constraints Generically

### 2015-02-12 paper/paper 2/paper 2.tex
5

We are able to offer the validation of all \emph{specific constraints} (expressed by any constraint language) by defining mappings from each \emph{specific constraint} to SPIN, 
what we have done for all OWL 2 and DSP constructs and for some constructs of other constraint languages (see section \ref{sec:implementation}).
%We do not have to define a mapping to SPIN for each specific constraint. 
%when we define a mapping to SPIN for each generic constraint.
We do not have to map each \emph{specific constraint} to SPIN and we get identical validation results for semantically equivalent \emph{specific constraints},
(1) if we map semantically equivalent \emph{specific constraints} to the corresponding \emph{generic constraint} and 
(2) if we map the \emph{generic constraint} to SPIN.
As a consequence, we only have to define one SPIN mapping for each constraint type corresponding to a requirement within the RDF validation requirements database.
19 of 74 RDF constraint types can be expressed by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
This means that there must be 76 (four for each constraint type) implementations to validate 76 \emph{specific constraints} - instead of only 19 implementations (one for each \emph{generic constraint}).

@@

@@

\section{Implementation}
\label{sec:implementation}

SPARQL is generally seen as the method of choice to validate RDF data according to certain constraints, although it is not ideal for their formulation. 
In contrast, OWL 2 and DSP constraints are comparatively easy to understand, but lack an implementation to validate RDF data. 
Bosch and Eckert\cite{BoschEckert2014-2} use SPIN as basis to define a
validation environment in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL. 
The validation implementation of constraint languages is fully declarative,
consisting of a mapping from constraint languages to SPIN in form of SPARQL CONSTRUCT queries.
SPIN represents both the SPIN mappings and the SPARQL queries in RDF. 
Within the validation environment, we fully implemented the validation of all OWL 2 DL\footnote{OWL to SPIN: \url{https://github.com/boschthomas/OWL2-SPIN-Mapping}} and DSP\footnote{DSP to SPIN: \url{https://github.com/dcmi/DSP-SPIN-Mapping}} constructs (for the complete DSP validation see \cite{BoschEckert2014-2}). 
The implementation can be tested at \url{http://purl.org/net/rdfval-demo}.
The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.

We provide a mapping from RDF-CO to SPIN\footnote{RDF-CV to SPIN: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}} in order to automatically validate each type of generic constraint (simple, complex, property, and class constraints).
Part of future work will be 
(1) to provide a GUI which generates generic constraints automatically according to inputs of domain experts who are not familiar with the formulation of constraints; 
(2) to offer bidirectional transformations between specific constraints (expressed by multiple constraint languages) and generic constraints;
(3) to provide translations between specific constraints (expressed by any specific constraint language) by using generic constraints as an intermediate transformation step.
%\begin{itemize}
	%\item to provide a GUI which generates generic constraints automatically according to inputs of domain experts who are not familiar with the formulation of constraints.
	%\item to offer bidirectional transformations between specific constraints (expressed by multiple constraint languages) and generic constraints. 
	%\item to provide translations between specific constraints (expressed by any specific constraint language) by using generic constraints as an intermediate transformation step.
%\end{itemize}
\section{Evaluation}
\label{sec:evaluation}

>>>>

SPARQL is generally seen as the method of choice to validate RDF data according to certain constraints, although it is not ideal for their formulation. 
In contrast, OWL 2, DSP, ReSh, and ShEx constraints are comparatively easy to understand. 
Bosch and Eckert \cite{BoschEckert2014-2} use SPIN as basis to define a
validation environment in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL
(the implementation can be tested at \url{http://purl.org/net/rdfval-demo}).
The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
We are able to offer the validation of all \emph{specific constraints} (expressed by any constraint language) by defining mappings from each \emph{specific constraint} to SPIN, 
what we have done for all OWL 2\footnote{OWL to SPIN: \url{https://github.com/boschthomas/OWL2-SPIN-Mapping}} and DSP\footnote{DSP to SPIN: \url{https://github.com/dcmi/DSP-SPIN-Mapping}} constructs and for some constructs of other constraint languages.
%We do not have to define a mapping to SPIN for each specific constraint. 
%when we define a mapping to SPIN for each generic constraint.
We do not have to map each \emph{specific constraint} to SPIN and we get identical validation results for semantically equivalent \emph{specific constraints},
(1) if we map semantically equivalent \emph{specific constraints} to the corresponding \emph{generic constraint} and 
(2) if we map the \emph{generic constraint} to SPIN.
As a consequence, we only have to define one SPIN mapping for each constraint type corresponding to a requirement within the RDF validation requirements database.
19 of 74 RDF constraint types can be expressed by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
This means that there must be 76 (four for each constraint type) implementations to validate 76 \emph{specific constraints} - instead of only 19 implementations (one for each \emph{generic constraint}).

%The validation implementation of constraint languages is fully declarative,
%consisting of a mapping from constraint languages to SPIN in form of SPARQL CONSTRUCT queries.
%SPIN represents both the SPIN mappings and the SPARQL queries in RDF. 
%Within the validation environment, we fully implemented the validation of all OWL 2 DL and DSP constructs 
%(for the complete DSP validation see \cite{BoschEckert2014-2}).

@@

We provide a mapping from the \emph{RDF-CV} to SPIN\footnote{RDF-CV to SPIN: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}} in order to automatically validate each type of \emph{generic constraint} (\emph{simple}, \emph{complex}, \emph{property}, and \emph{class constraints}).
Part of future work will be 
(1) to provide a GUI which generates \emph{generic constraints} automatically according to inputs of domain experts who are not familiar with the formulation of constraints,
(2) to offer bidirectional transformations between \emph{specific constraints} (expressed by multiple constraint languages) and \emph{generic constraints}, and
(3) to provide translations between semantically equivalent \emph{specific constraints} (expressed by any constraint language) by using \emph{generic constraints} as an intermediate transformation step.
%\begin{itemize}
	%\item to provide a GUI which generates generic constraints automatically according to inputs of domain experts who are not familiar with the formulation of constraints.
	%\item to offer bidirectional transformations between specific constraints (expressed by multiple constraint languages) and generic constraints. 
	%\item to provide translations between specific constraints (expressed by any specific constraint language) by using generic constraints as an intermediate transformation step.
%\end{itemize}

@@

\section{Evaluation}
\label{sec:evaluation}
